---
title: "Package Development Lab Day 1"
author: "Joyce Robbins"
output:
  github_document:
    default
  pdf_document:
    default
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

# Create a package

1. Create the package

```{r}
library(devtools)
# adjust the path as you wish, just don't create a package
# inside another project, package, or repo
create_package("~/covidtime")  
```


2. Create the following function and save it as `day.R` in the R folder:

```{r}
whatdayisit <- function() {
  format(Sys.Date(), "%A, %B %d, %Y")
}
```

3. Run:

```{r}
library(devtools)
load_all()
```

4. Test the function:

```{r}
whatdayisit()
```

5. Make some changes and repeat 3. and 4.


# Document and install

1. Edit `DESCRIPTION`

It should look something like this, with *your* name and email address. *Don't remove what looks like an extra comma in* `Authors@R`.

```
Package: covidtime
Title: Helps reduce pandemic induced temporal disintegration
Version: 0.0.0.9000
Authors@R: 
    person("first", "last", , "first.last@example.com", role = c("aut", "cre"))
Description: Tools for regaining temporal orientation.
License: `use_mit_license()`, `use_gpl3_license()` or friends to pick a
    license
Encoding: UTF-8
Roxygen: list(markdown = TRUE)
RoxygenNote: 7.1.2
```

2. Open `day.R`. Put the cursor inside the function and click "Code... Insert Roxygen Skeleton". Add to the documentation so it looks something like this:

```
#' Returns the current day and date nicely formatted
#'
#' @return character string with day and date
#' 
#' @export
#'
#' @examples
#' whatdayisit()
#' 
```

3. Run:

```{r}
document()
```

4. Run:

```{r}
install()
```

Check that it appears in your list of packages. 

5. Close the project and try using your package!

```{r}
library(covidtime)
whatdayisit()
```

