---
title: "Package Development Lab Day 2"
author: "Joyce Robbins"
output:
  github_document:
    default
  pdf_document:
    default  
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```


# Create a package (only if you missed Day 1)

OR: fork and clone: https://github.com/jtr13/covidtime

1. Create the package file structure by typing the following in the Console. Choose the path carefully so that you don't create a package inside another project. 

```{r}
library(devtools)
create_package("~/covidtime")  # you can change the path
```

Your RStudio session will now switch to the new `covidtime` package project.


2. Create a new R script, type in the following function, and save it as `day.R` in the R folder:

```{r}
whatdayisit <- function() {
  format(Sys.Date(), "%A, %B %d, %Y")
}
```

# New Stuff

## Dependencies

Add a line to `whatdayisit()` that indicates the number of days to the next month using `lubridate::rollforward()`.

Run `usethis::use_package("lubridate")`.

```{r}
whatdayisit <- function() {
  paste0("Today is ",
         format(Sys.Date(), "%A, %B %d, %Y"),
         ". There are ", 
         as.numeric(lubridate::rollforward(Sys.Date()) - Sys.Date()),
         " days until next month.")
         }
```




## Checking

Run `devtools::check()` or click "Check" in the build pane.

## Add a license

Run `usethis::use_mit_license("Your name")`


## Functions

Create a `whenis(month)` function in **covidtime** that returns the number of days until the month indicated. `month` should be entered as a three letter abbreviation.

```
> whenis("Jul")
Time difference of 169 days
```

```{r}
whenis <- function(month) {
  year <- lubridate::year(Sys.Date())
  monthdate <- as.Date(paste0(year, "-", which(month.abb == month), "-01"))
  if (monthdate < Sys.Date()) {
    monthdate <- as.Date(paste0(year + 1, "-", which(month.abb == month), "-01"))
  }
  paste(month.name[which(month.abb == month)], "will arrive in", monthdate - Sys.Date(), "days.")
}
```


## Run-time testing

Use `if( )... stop()` to stop execution if `month` isn't a three letter month abbreviation and provide useful information.

```{r}
whenis <- function(month) {
  if (!(month %in% month.abb)) stop("The month must be entered as a three letter abbreviation: ", paste(month.abb, collapse = " "))
  year <- lubridate::year(Sys.Date())
  monthdate <- as.Date(paste0(year, "-", which(month.abb == month), "-01"))
  if (monthdate < Sys.Date()) {
    monthdate <- as.Date(paste0(year + 1, "-", which(month.abb == month), "-01"))
  }
  paste(month.name[which(month.abb == month)], "will arrive in", monthdate - Sys.Date(), "days.")
}
```