---
title: "Package Development Lab Day 2"
author: "Joyce Robbins"
output:
  github_document:
    default
  pdf_document:
    default  
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```


# Create a package (only if you missed Day 1)

OR: fork and clone: https://github.com/jtr13/covidtime

1. Create the package file structure by typing the following in the Console. Choose the path carefully so that you don't create a package inside another project. 

```{r}
library(devtools)
create_package("~/covidtime")  # you can change the path
```

Your RStudio session will now switch to the new `covidtime` package project.


2. Create a new R script, type in the following function, and save it as `day.R` in the R folder:

```{r}
whatdayisit <- function() {
  format(Sys.Date(), "%A, %B %d, %Y")
}
```

# New Stuff

## Dependencies

Add a line to `whatdayisit()` that indicates the number of days to the next month using `lubridate::rollforward()`.

Run `usethis::use_package("lubridate")`.

## Checking

Run `devtools::check()` or click "Check" in the build pane.

## Add a license

Run `usethis::use_mit_license("Your name")`


## Functions

Create a `days_to(month)` function in **covidtime** that returns the number of days until the month indicated. `month` should be entered as a three letter abbreviation.

```
> daysto("Jul")
Time difference of 169 days
```

## Run-time testing

Use `if( )... stop()` to stop execution if `month` isn't a three letter month abbreviation and provide useful information.

